Scalable statistical genetic data analysis in Python

### 2024-01-09 paper.tex
Add figure PDFs and systematics data file names
Minor tweaks

Here is a quick rundown of the sections and what they do:

@@

\end{minted}
\end{tcolorbox}
\end{tabular}
\caption{Whole-matrix compute performance with increasing sample size.
(A) Total CPU time required to run the afdist calculation for
a subset of 10 samples and 10000 variants from the middle of the matrix.
(B) Same for n/2 samples. Genozip did not run in this case for
$n > 10^4$ samples because it does not support a file to specify
sample IDs, and the command line was therefore too long for the shell
to execute.
(C) A simplified version of the source code used for these benchmarks.
\label{fig-subset-matrix-compute}}
\end{figure*}

@@

\section*{Text graveyard}

>>>>

\subsection{Overview of narrative for draft}
This subsection is a high-level summary of the main sections and 
their narrative connections. \textbf{The section is for authors only and 
will be deleted 
once the sections themselves have matured reasonably}

@@

\end{minted}
\end{tcolorbox}
\end{tabular}
\caption{Compute performance on subsets of the matrix.
(A) Total CPU time required to run the afdist calculation for
a subset of 10 samples and 10000 variants from the middle of the matrix.
(B) Same for n/2 samples. Genozip did not run in this case for
$n > 10^4$ samples because it does not support a file to specify
sample IDs, and the command line was therefore too long for the shell
to execute.
(C) A simplified version of the source code used for these benchmarks.
\label{fig-subset-matrix-compute}}
\end{figure*}

@@

\clearpage
\section*{Text graveyard}
